\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}

\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}

\begin{document}

\begin{center}
  \begin{minipage}{\textwidth}
    \centering
    {\LARGE\textbf{Eyup Bayram}} \hspace{2pt} {\LARGE Backend Engineer}\\[8pt]
    Umraniye, Istanbul \textbullet\ 
    \href{mailto:egorkemb@gmail.com}{egorkemb@gmail.com} \textbullet\
    +90 505 554 84 58 \textbullet\
    \href{https://linkedin.com/in/egbayram}{linkedin.com/in/egbayram} \textbullet\
    \href{https://github.com/egbay}{github.com/egbay}
  \end{minipage}
\end{center}

\section{Summary}
Backend-heavy software engineer (7+ yrs) focused on AI products and cloud-native architectures with hands-on backend experience (Python/FastAPI, Node/NestJS, PostgreSQL). Designed reliable billing pipelines and low-latency APIs on AWS/Lambda/edge, with strong focus on observability and safe rollouts. Looking to drive platform reliability and developer velocity in a backend/platform role. Passionate about leveraging technology to solve real-world problems and contribute to impactful projects.

\section{Experience}

\textbf{Freelancer}. \textit{Backend Engineer} \hfill Jul 2024 -- Present\\
\textit{Istanbul, Türkiye (Remote)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item \textbf{Project: Payments \& Billing + Online Learning Platform} --- Modeled DB with Prisma; managed schema migrations and transactions; implemented repository/service layers to ensure data integrity. Stack: NestJS, TypeScript, Prisma, PostgreSQL.
  \item \textbf{Project: AI Fashion Project} --- Developed REST APIs for model invocations, job management, and status tracking using FastAPI. Integrated Supabase authentication \& storage; enforced signed URLs and access policies. Built async workflows and queuing for long-running jobs. Deployed on GCP.
  \item \textbf{Project: Full-Stack Development for Multiple AI Products} --- Defined service boundaries, API contracts, and inter-service communication (HTTP/queues) in a microservice architecture. Used FastAPI, Django, Node.js, TypeScript, Prisma across products. Built event-driven workflows and serverless functions on AWS Lambda. Rapidly shipped UI with Vercel V0 and hardened React components for production.
  \item \textbf{Key Achievements:}
    \begin{itemize}[leftmargin=1.2em,noitemsep,topsep=0pt]
      \item Shipped a modular billing architecture enabling easy addition of new plans and discount rules.
      \item Increased resilience with idempotency and retry patterns on critical payment operations.
      \item Implemented RBAC-based authorization with clear customer/teacher/student boundaries.
      \item Modular job/pipeline design enabled adding new AI variants with minimal changes.
      \item Established data lifecycle and access policies to protect customer assets.
      \item Achieved low latency and effortless scaling via serverless and edge patterns; adopted feature flags for safe rollouts.
    \end{itemize}
\end{itemize}

\textbf{Smartex AI}. \textit{Backend Engineer \& Managing Director} \hfill Sep 2022 -- Jul 2024\\
\textit{Porto, Portugal}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Led Smartex’s expansion in Türkiye post-acquisition of Tuvis AI, managing budgets, compliance, and resourcing.
  \item Backend development with Node.js, TypeScript, PostgreSQL, MongoDB, TypeORM, Prisma; key role in migration from TypeORM to Prisma.
  \item Owned production support: created API endpoints, resolved live bugs, and improved operational stability.
  \item \textbf{Key Achievements:} Strengthened regional presence and client relations; contributed to efficient backend solutions supporting the company’s \$40M+ funding milestones.
\end{itemize}

\textbf{Tuvis AI}. \textit{Co-Founder \& Software Engineer} \hfill Jul 2018 -- Sep 2022\\
\textit{Istanbul, Türkiye}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Co-founded and scaled AI-driven anomaly detection solutions for manufacturing process optimization.
  \item Led a team across project planning, technical implementation, and server management.
  \item Hands-on backend work with Flask, Django, PostgreSQL, Redis, AWS (S3, EC2, RDS, Lambda, CloudWatch, ECR), GitHub Actions, Celery, RabbitMQ.
  \item Engaged clients with technical insights; secured multiple R\&D projects funded by TUBITAK, KOSGEB, and Growth Circuit VC.
  \item \textbf{Key Achievements:} Enabled Tuvis AI acquisition by Smartex.ai (2023); delivered high CSAT and long-term partnerships.
\end{itemize}

\textbf{Peakode}. \textit{Research \& Development Engineer (Part-Time)} \hfill Sep 2016 -- Jun 2017\\
\textit{Bursa, Türkiye}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Built IoT solutions with XBee sensor networks, xCTU, Node.js, and Raspberry Pi.
\end{itemize}

\textbf{TOFAS}. \textit{Research \& Development Engineer (Part-Time)} \hfill Sep 2016 -- Jun 2017\\
\textit{Bursa, Türkiye}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Conducted CAN Bus analysis and contributed to Instrument Cluster Panel development for an EV prototype using C++ and GLStudio.
  \item Awarded ``Best R\&D Project'' within TOFAS.
\end{itemize}

\section{Education \& Certifications}
\textbf{Kocaeli University} \hfill Kocaeli, Türkiye\\
\textit{M.Sc. in Computer Engineering} \hfill Jan 2019 -- Thesis Stage\\[4pt]
\textbf{Emerald Cultural Institute} \hfill Dublin, Ireland\\
\textit{Academic English Program (IELTS 6.5)} \hfill Oct 2017 -- Jun 2018\\[4pt]
\textbf{Uludag University} \hfill Bursa, Türkiye\\
\textit{B.Sc. in Electrical \& Electronics Engineering} \hfill Sep 2013 -- Jun 2017\\[6pt]
\textbf{IELTS Academic (6.5)} \hfill Feb 2018

\section{Skills}
\textbf{Languages:} Python, JavaScript/TypeScript\\
\textbf{Databases:} MySQL, PostgreSQL, MongoDB\\
\textbf{Frameworks:} Flask, FastAPI, Django, Node.js, NestJS, Prisma, TypeORM\\
\textbf{Cloud/Tech:} Serverless Framework, AWS (S3, SNS, EC2, API Gateway, Lambda, RDS, CodeCommit, CloudWatch)\\
\textbf{Other:} Celery, Redis, RabbitMQ, GitHub Actions, Sentry, CAN Bus\\
\textbf{Language Proficiency:} English (IELTS 6.5)

\section{Volunteer}
Co-founded the IEEE Bursa Uludag University Student Branch; organized events, workshops, and technical trainings to help students build leadership and engineering skills.

\end{document}
